An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-04-08 mixedwindow.tex
Add NBER-NSF conference to acknowledgements

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft \protect\url{http://gray.clhn.co}\guillemotright.
    I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Allan Timmermann, Stephane
    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
    Group meeting for helpful comments and discussions.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    RFS paper with Ivo Welch \citep{GoW:08}.}\\%
  Iowa State University}

>>>>

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft \protect\url{http://gray.clhn.co}\guillemotright.
    I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Allan Timmermann, Stephane
    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
    Group meeting and the 2013 NBER-NSF Time Series conference
    for helpful comments and discussions.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    RFS paper with Ivo Welch \citep{GoW:08}.}\\%
  Iowa State University}
